Lateral Inhibition Nets with Nonlinear Connections

### 2017-05-02 paper.tex
architecture done

\subsection{Input Determined Sparsity}
In fact, we may present the computing flow for each filter as the transformations of its feature map,
$$\mathbf{X}\longmapsto\cdots\longmapsto\Phi_{p_i}\overset{\Omega(r)}{\longmapsto}\Phi_{p_i}'\overset{\Psi(r,\beta,\theta)}{\longmapsto}\Phi_{p_i}''$$,
with $\Psi$ defined as the binarization phase. We take $\Phi_{p_i}'$ as the final state of feature map generated by
filter $\mathcal{F}_{p_i}$, and $\Phi_{p_i}''$ is the mask of its sparsity.
Obviously, $\Phi_{p_i}''$ is determined by its input $\mathbf{X}$, which may be an original image.
For each different input of a net, the sparsity mask may vary, and this is different from the Dropout\cite{hinton2012improving}
and Dropconnect\cite{wan2013regularization} regularization, which randomly reduce nodes or connections to train submodels of a net.

@@

>>>>

\subsection{Input Determined Sparsity}
In fact, we may present the computing flow for each filter as the transformations of its feature map,
$$\mathbf{X}\longmapsto\cdots\longmapsto\Phi_{p_i}
\overset{\Omega(r)}{\longmapsto}\Phi_{p_i}'
\overset{\Psi(r,\beta,\theta)}{\longmapsto}\Phi_{p_i}''$$
in which, let $\Psi$ be the binarization phase.
We take $\Phi_{p_i}'$ as the final state of feature map generated by
filter $\mathcal{F}_{p_i}$, and $\Phi_{p_i}''$ is the mask of its sparsity.
Obviously, $\Phi_{p_i}''$ is determined by its input $\mathbf{X}$, which may be an original image.
For each different input of a net, the sparsity mask may vary,
and this is different from the Dropout\cite{hinton2012improving}
and Dropconnect\cite{wan2013regularization} regularization, which randomly
reduce nodes or connections in a training iteration to train submodels of a net,
and consequently leading to literally twice the time cost on training\cite{hinton2012improving}.

Our method to make a net sparse relies totally on input patterns, not randomly choosing a
subset of the net model. As the feature map binarization phase indicates, it highlights
the receptive fields which have stronger responses to the input patterns,
and inhibites the others. This functionality is similarly to that of
\emph{Non-maximum suppression, NMS}\cite{dalal2005histograms}, which works well
in RCNNs and Mask-RCNNs\cite{girshick2014rich} to get best position proposals of
objects in images. While the difference is the binarization phase in our model
does not reduce those non-maximum nodes, but keeps the majority features with
far less nodes. Thus the net made sparse with binarization phase is neither a submodel
of the original net, nor a best-object-position-proposal aided model. Our model simply
aims to reduce the redundancy of connections and speed up the training process.

\begin{figure}
\centering
\includegraphics[width=85mm]{paper_res/arch.png}
\caption{An example of overall architectures}
\label{fig:net}
\end{figure}

For a general net of CNNs with $M$ convlayers(convolutonal layers),
we may assume that it has $N_{p}$ filters for a convlayer at depth $p$,
thus the volume of connections for this net is $O(\max(\{N_p\mid p=1,2,\cdots,M\})...)$,
With the binarization phase, we generate sparsity masks for every convlayer.
The overall architecture of our model is something like Fig-(\ref{fig:net}).

@@

\bibitem{dalal2005histograms}
N.~Dalal and B.~Triggs, ``Histograms of oriented gradients for human
detection,'' in \emph{Computer Vision and Pattern Recognition, 2005. CVPR
2005. IEEE Computer Society Conference on}, vol.~1.\hskip 1em plus 0.5em
minus 0.4em\relax IEEE, 2005, pp. 886--893.

\bibitem{girshick2014rich}
R.~Girshick, J.~Donahue, T.~Darrell, and J.~Malik, ``Rich feature hierarchies
for accurate object detection and semantic segmentation,'' in
\emph{Proceedings of the IEEE conference on computer vision and pattern
recognition}, 2014, pp. 580--587.
